Delocalization of Eigenvectors in Random Matrices

### 2025-03-24 Draft.tex
now typos

\end{tikzpicture}. With this, we have verified that all the partial derivative terms satisfy the estimate $O(W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}})$. 
\subsubsection*{Combined bound}
All of the latter graph expansions allowed us to confirm the following result: $$\max_{a,b}\max_{i=1, \cdots, 4}\max_{j=0, 1, 2, 3} \left\vert \int_0^{t\wedge \tau_\sto}\mathcal{G}_{ij, s}(z)_{ab}ds\right\vert\lesssim W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$$
It is important to note that so far we have been working with the loop and regular vertex expansions without the regularization terms. Their bounds require more technical tools that work with isotropic bounds on graph modifications, and as such was outside the scope of this thesis. We simply state that the implication of their result (Lemma 22 \cite{bandSDE}) is within the stochastic bound we established above. As such, we can conclude that when we integrate the graph \hyperref[graph]{$(6)$} we started with over $s\in [0, t\wedge \tau_\sto]$ is $\prec W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$, given that all of the component terms in its sum expansion are of that order. Observe that everything we did applies WLOG to its conjguate, given that all of the bounds are the same. This in fact means that: $$\max_{a, b}\left\vert \int_0^{\tau_\sto\wedge t} \{\text{Id} + (t-s)\Theta_t\} S^{1/2}\Omega_s(z)S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds\right\vert \prec W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$$
The authors then argue that by virtue of "naive polynomial-in-W bounds" for the LHS and a "standard net argument" \cite{bandSDE} one can conclude:\begin{boxtheorem}{Theorem 6.1}
$$\max_{t\in [0, 1]}\max_{a, b}\frac{\left\vert \int_0^{\tau_\sto\wedge t} \{\text{Id} + (t-s)\Theta_t\} S^{1/2}\Omega_s(z)S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds\right\vert }{W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}}\prec 1$$\end{boxtheorem}
While the technical details are again outside of the scope of thesis, we can elaborate on the meaning of both those approaches. The first one refers to straightforward power counting of each matrix component in the integrand. Specifically, $[\text{Id} + (t - s)\Theta_t]$ contributes at most $O(1)$ since $t,s \in [0,1]$ and $\Theta_t$ has bounded entries. The matrices $S_t^{\frac{1}{2}}$, $\Omega_s(z)$, and $S_s^{\frac{1}{2}}$ each contribute additional powers of $W$, but their product maintains an overall scaling of $O(W^C)$ where $C\lesssim 1$ does not depend on $W$. The net argument, on the other hand, provides control over the supremum by discretizing the integration interval $[0, \tau_{\text{stop}} \wedge t]$ into an $\varepsilon$-net with spacing $\delta = W^{-D}$ for some appropriate constant $D$. At each point in this net, one establishes the aforementioned $O(W^C)$ bound, and by continuity of the integrand (with Lipschitz constant also polynomially bounded in $W$), these bounds extend to the entire interval with negligible error. When normalized by the denominator $W^{-\frac{3}{4}}\eta_t^{-1} \cdot W^{-1}\eta_t^{-\frac{1}{2}}$, the ratio remains bounded by a constant, and as such, is $\prec 1$.

@@

\begin{boxtheorem}{Theorem 1: (Stopping time).} $\mathbb{P}[\tau_{\text{stop}, i} \neq  1] \lesssim_D N^{-D}$ for any $i=1, 2$ and $D > 0$.
\end{boxtheorem}
\textit{Proof} - By Boole's inequality: $$\mathbb{P}\left[\tau_{\sto, 1}\neq 1\right]\leq \mathbb{P}[\left\{\tau_{\sto, 2}\neq 1\}\cap \{\tau_{\sto, 1=1}\}\right]+\mathbb{P}[\tau_\sto=\tau_{\sto, 1}<1]$$
For any $\mathcal{A}\in \{\tau_\sto = \tau_{\sto, 1}<1\}$, we have $|\E_{\tau_\sto}(z)_{ab}|\geq W^{\delta_\sto}W^{-3/4}\eta_t^{-1}W^{-1}\eta_t^{-1/2}$, since $\E_t(z)$ is almost surely continuous in $t$. By definition of the stopped SDE, we have $\E_{\tau_\sto}(z) = \E_{\tau_\sto}^{\sto}(z)$, i.e: $$\mathbb{P}\left[\tau_\sto = \tau_{\sto, 1}<1\right]\leq \mathbb{P}\left[\max_{t\in [0, 1]}\max_{a, b}\frac{|\E_t^{M, \sto}(z)_{ab}|}{W^{-\frac{3}{4}}\eta_t^{-\frac{3}{4}}W^{-1}\eta_t^{-\frac{1}{2}}}\geq W^{\delta_\sto}\right]$$
By our theorems $6.1$ through $6.3$ in the last section applied to the RHS, we know from the definition of stochastic domination that for any $D>0$: 
$$\mathbb{P}\left[ \tau_\sto = \tau_{\sto, 1}<1\right]\leq C_DN^{-D}$$
This means that we know need to establish an equivalent bound for the first term on the RHS. Assume an event $\mathcal{B}$ for which the following is true:
$$\max_{t\in [0, 1]}\max_{a, b}\frac{|\E_t(z)_{ab}|}{W^{\delta_\sto}W^{-\frac{3}{4}}\eta_t^{-\frac{3}{4}}W^{-1}\eta_t^{-\frac{1}{2}}}\lesssim 1$$
Since $T_t(z) = \Theta_t+\E_t(z)$ and $|(\Theta_t)_{ab}|\lesssim W^{-1}\eta_t^{-1/2}$ (Lemma A.2), this implies that on $\mathcal{B}$, we have $T_t(z)_{ab}\lesssim W^{-1}\eta_t^{-\frac{1}{2}}$. By the behavior of $S^{1/2}$ as an averaging operator, we have for all $a, b$ and $t\in [0, 1]$: $$(S^{1/2}T_t(z)S^{1/2})_{ab}\lesssim W^{-1}\eta_t^{-1/2}.$$ 
This means that by \hyperref[corollary-b5]{Corollary B.5} on the event $\mathcal{B}$, we get precisely: $$\frac{|G_t(z)_{ab}-m(z)\delta_{ab}|}{(S^{1/2}T_t(z)S^{1/2})_{ab}+S^{1/2}_{ab}+W^{-C}}\prec 1$$
Hence, $\mathbb{P}[\left\{\tau_{\sto, 2}\neq 1\}\cap \{\tau_{\sto, 1=1}\}\right]\rightarrow 0$ as $N\rightarrow \infty$, completing the theorem.

@@

\subsection*{7.3 Theorem 3}
\label{proof-deloc}
\begin{boxtheorem}{Theorem 3}
\noindent Assume $|E|<2$ is fixed and that $\exists \nu>0$, s.t. $\eta \asymp W^2 N^{-2}$ and $W\geq N^{8/11+\nu}$. Then:
\begin{center}$\max_{x, y}|G_{xy} - \delta_{xy}m(z)|^2\prec W^{-1}\eta^{-\frac{1}{2}}$\end{center}
\end{boxtheorem}
\textit{Proof} - By Theorem 1 and the definition $(3.4.2)$ of $\tau_\sto$, we have that: $$\max_{x, y}|G_{xy} - \delta_{xy}m(z)|^2\prec \max_{a, b}(S^{1/2}T_1(z)S^{1/2})_{ab}+\max_{a, b}S_{ab}^{1/2}$$
By Theorem 2 we showed above, \hyperref[lemma-a2]{Lemma A2}, and the behavior of $S^{1/2}$ as the averaging operator: $$\max_{a, b}T_1(z)_{ab}\prec W^{_1}\eta_1^{-1/2} = W^{-1}\eta^{-1/2}\Rightarrow \max_{ab}\left(S^{1/2}T_1(z)S^{1/2}\right)_{ab}\prec W^{-1}\eta^{-1/2}$$
$$\Rightarrow \max_{x, y}|G_{xy} - \delta_{xy}m(z)|^2\prec  W^{-1}\eta^{-1/2}+W^{-1}\prec  W^{-1}\eta^{-1/2}$$
\newpage
\subsection*{7.4 Theorem 4 - Delocalization}
\begin{boxtheorem}{Theorem 4: (Delocalization).}
For any $\ell\ll N$ and fixed $\epsilon, \kappa, c>0$: $$\frac{|\mathcal{A}_{\epsilon, \ell, \kappa}|}{N}\lesssim \sqrt{\epsilon}+\mathcal{O}(N^{-c})$$
\end{boxtheorem}
\textit{Proof} - The following proof is entirely due to Erd\H{o}s, et. al. \cite{21}, where it appears as Proposition 7.1. We present it here in order to better understand the nature of delocalization. The authors assume that $\Lambda(z) = \max_{x, y}|G_{xy}(z)-\delta_{xy}m(z)|\prec \Psi$, where $\Psi$ is a deterministic admissible parameter if $M^{-1/2}\leq \Psi^{(N)}(z)\leq M^{-\gamma/2}$ for all $N$, $E\in (2, 2)$ and $\eta\in M^{-1+\gamma}\leq \eta\leq 10)$, where $M = \frac{1}{\max_{i, j}S_{ij}}$. In the context of the work by Dubova and Yang we have presented so far, these assumptions are satisfied, given that Theorem 4 implies $|G_{xy}(z)-\delta_{xy}m(z)|^2\prec W^{-1}\eta^{-1/2}\lesssim N^{-1}\eta^{-1}$ by using the global diffusion scale $\eta\asymp W^2 N^{-2}$. Furthermore, by the other assumption $N\ll W^{11/8}$, one has $N^{-1}\eta^{-1}\asymp NW^{-1}\ll W^{-5/8}$\cite{bandSDE}. Namely, by Ward and the latter admissible parameter, we have for all $x$: \begin{equation*}\frac{\eta}{\im m}\sum_y|G_{yx}|^2 = \frac{\im G_{xx}}{\im m}\lesssim 1+O(N^{-1}\eta^{-1})\tag{7.4.1}\end{equation*}
uniformly in $E$. Hence, the map $y\mapsto \frac{\eta}{\im m(z)}|G_{yx}|^2$ is approximately a PDF on $\Gamma$, yielding:
$$\frac{\eta}{\im m(z)}\|P_{x, \ell}G \mathbf{e}_x\|^2 = \frac{\eta}{\im m(z)}\sum_y \mathbf{1}\left(|y-x|\geq \ell\right)|G_{yx}|^2=$$
$$=\frac{\eta}{\im m(z)}\sum_y|G_{yx}|^2 - \frac{\eta}{\im m(z)}\sum_y \mathbf{1}\left(|y-x|\geq \ell\right)|G_{yx}|^2=1+O(N^{-c}),$$
for some $c>0$ by using Theorem 4, Lemma B.1 and $(7.4.1)$. Using the spectral decomposition $(1.1)$: 
$$\frac{\eta}{\im m(z)} \|P_{x, \ell} G\mathbf{e}_x\|^2 = \frac{\eta}{\im m(z)}\left\|\sum_\alpha \frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)P_{x, \ell}\mathbf{u}_\alpha\right\|^2\leq $$
$$\leq \frac{\eta}{\im m(z)}\left(1+\frac{1}{\xi}\right)\left\|\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}\frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)P_{x, \ell}\mathbf{u}_\alpha\right\|^2 +  \frac{\eta}{\im m(z)}\left(1+\frac{1}{\xi}\right)\left\|\sum_{\alpha\in \mathcal{A}^C_{\epsilon, \ell}}\frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)P_{x, \ell}\mathbf{u}_\alpha\right\|^2,$$
where $\xi>0$ is arbitrary and $\mathcal{A}^C_{\epsilon, \ell} =\{1, \cdots, N\}\backslash A_{\epsilon, \ell}$ is the complement set.

>>>>

\end{tikzpicture}. With this, we have verified that all the partial derivative terms satisfy the estimate $O(W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}})$. 
\subsubsection*{Combined bound}
All of the latter graph expansions allowed us to confirm the following result: $$\max_{a,b}\max_{i=1, \cdots, 4}\max_{j=0, 1, 2, 3} \left\vert \int_0^{t\wedge \tau_\sto}\mathcal{G}_{ij, s}(z)_{ab}ds\right\vert\lesssim W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$$
It is important to note that so far we have been working with the loop and regular vertex expansions without the regularization terms. They require more technical tools that work with isotropic bounds on graph modifications, and as such was outside the scope of this thesis. We simply state that the implication of their result (Lemma 22 \cite{bandSDE}) is within the stochastic bound we established above. As such, we conclude that when we integrate the graph \hyperref[graph]{$(6)$} over $s\in [0, t\wedge \tau_\sto]$, we get $\prec W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$, given that all of the component terms in its sum expansion are of that order. Observe that everything we did applies WLOG to its conjguate, given that all of the bounds are the same, hence: $$\max_{a, b}\left\vert \int_0^{\tau_\sto\wedge t} \{\text{Id} + (t-s)\Theta_t\} S^{1/2}\Omega_s(z)S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds\right\vert \prec W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$$
The authors then argue that by virtue of "naive polynomial-in-W bounds" for the LHS and a "standard net argument" \cite{bandSDE} one can conclude:\begin{boxtheorem}{Theorem 6.1}
$$\max_{t\in [0, 1]}\max_{a, b}\frac{\left\vert \int_0^{\tau_\sto\wedge t} \{\text{Id} + (t-s)\Theta_t\} S^{1/2}\Omega_s(z)S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds\right\vert }{W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}}\prec 1$$\end{boxtheorem}
While the technical details are again outside of the scope of thesis, we can elaborate on the meaning of both those approaches. The first one refers to straightforward power counting of each matrix component in the integrand. Specifically, $[\text{Id} + (t - s)\Theta_t]$ contributes at most $O(1)$ since $t,s \in [0,1]$ and $\Theta_t$ has bounded entries. The matrices $S_t^{\frac{1}{2}}$, $\Omega_s(z)$, and $S_s^{\frac{1}{2}}$ each contribute additional powers of $W$, but their product maintains an overall scaling of $O(W^C)$ where $C\lesssim 1$ does not depend on $W$. The net argument, on the other hand, provides control over the supremum by discretizing the integration interval $[0, \tau_{\text{stop}} \wedge t]$ into an $\varepsilon$-net with spacing $\delta = W^{-D}$ for some appropriate constant $D$. At each point in this net, one establishes the aforementioned $O(W^C)$ bound, and by continuity of the integrand (with Lipschitz constant also polynomially bounded in $W$), these bounds extend to the entire interval with negligible error. When normalized by the denominator $W^{-\frac{3}{4}}\eta_t^{-1} \cdot W^{-1}\eta_t^{-\frac{1}{2}}$, the ratio remains bounded by a constant, and as such, is $\prec 1$.

@@

\begin{boxtheorem}{Theorem 1: (Stopping time).} $\mathbb{P}[\tau_{\text{stop}, i} \neq  1] \lesssim_D N^{-D}$ for any $i=1, 2$ and $D > 0$.
\end{boxtheorem}
\textit{Proof} - By Boole's inequality: $$\mathbb{P}\left[\tau_{\sto, 1}\neq 1\right]\leq \mathbb{P}[\left\{\tau_{\sto, 2}\neq 1\}\cap \{\tau_{\sto, 1=1}\}\right]+\mathbb{P}[\tau_\sto=\tau_{\sto, 1}<1]$$
For any $\mathcal{A}\in \{\tau_\sto = \tau_{\sto, 1}<1\}$, we have $|\E_{\tau_\sto}(z)_{ab}|\geq W^{\delta_\sto}W^{-3/4}\eta_t^{-1}W^{-1}\eta_t^{-1/2}$, since $\E_t(z)$ is almost surely continuous in $t$. By definition of the stopped SDE, we have $\E_{\tau_\sto}(z) = \E_{\tau_\sto}^{\sto}(z)$, i.e: $$\mathbb{P}\left[\tau_\sto = \tau_{\sto, 1}<1\right]\leq \mathbb{P}\left[\max_{t\in [0, 1]}\max_{a, b}\frac{|\E_t^{M, \sto}(z)_{ab}|}{W^{-\frac{3}{4}}\eta_t^{-\frac{3}{4}}W^{-1}\eta_t^{-\frac{1}{2}}}\geq W^{\delta_\sto}\right]$$
By applying our theorems $6.1$ through $6.3$ to the RHS, we know from the definition of stochastic domination that for any $D>0$: 
$$\mathbb{P}\left[ \tau_\sto = \tau_{\sto, 1}<1\right]\leq C_DN^{-D}$$
This means that we know need to establish an equivalent bound for the first term on the RHS. Assume $\exists \mathcal{B}$ an event for which the following is true:
$$\max_{t\in [0, 1]}\max_{a, b}\frac{|\E_t(z)_{ab}|}{W^{\delta_\sto}W^{-\frac{3}{4}}\eta_t^{-\frac{3}{4}}W^{-1}\eta_t^{-\frac{1}{2}}}\lesssim 1$$
Since $T_t(z) = \Theta_t+\E_t(z)$ and $|(\Theta_t)_{ab}|\lesssim W^{-1}\eta_t^{-1/2}$ (Lemma A.2), this implies that on $\mathcal{B}$, we have $T_t(z)_{ab}\lesssim W^{-1}\eta_t^{-\frac{1}{2}}$. By the behavior of $S^{1/2}$ as an averaging operator, we have for all $a, b$ and $t\in [0, 1]$: $$(S^{1/2}T_t(z)S^{1/2})_{ab}\lesssim W^{-1}\eta_t^{-1/2}.$$ 
This means that by \hyperref[corollary-b5]{Corollary B.5} on the event $\mathcal{B}$, we get precisely: $$\frac{|G_t(z)_{ab}-m(z)\delta_{ab}|}{(S^{1/2}T_t(z)S^{1/2})_{ab}+S^{1/2}_{ab}+W^{-C}}\prec 1$$
Hence, $\mathbb{P}[\left\{\tau_{\sto, 2}\neq 1\}\cap \{\tau_{\sto, 1=1}\}\right]\rightarrow 0$ as $N\rightarrow \infty$, completing the theorem.

@@

\subsection*{7.3 Theorem 3}
\label{proof-deloc}
\begin{boxtheorem}{Theorem 3}
\noindent Assume $|E|<2$ is fixed and that $\exists \nu>0$, s.t. $\eta \asymp W^2 N^{-2}$ and $W\geq N^{8/11+\nu}$. Then:
\begin{center}$\max_{x, y}|G_{xy} - \delta_{xy}m(z)|^2\prec W^{-1}\eta^{-\frac{1}{2}}$\end{center}
\end{boxtheorem}
\textit{Proof} - By Theorem 1 and the definition $(3.4.2)$ of $\tau_\sto$, we have that: $$\max_{x, y}|G_{xy} - \delta_{xy}m(z)|^2\prec \max_{a, b}(S^{1/2}T_1(z)S^{1/2})_{ab}+\max_{a, b}S_{ab}^{1/2}$$
By Theorem 2 we showed above, \hyperref[lemma-a2]{Lemma A2}, and the behavior of $S^{1/2}$ as the averaging operator: $$\max_{a, b}T_1(z)_{ab}\prec W^{_1}\eta_1^{-1/2} = W^{-1}\eta^{-1/2}\Rightarrow \max_{ab}\left(S^{1/2}T_1(z)S^{1/2}\right)_{ab}\prec W^{-1}\eta^{-1/2}$$
$$\Rightarrow \max_{x, y}|G_{xy} - \delta_{xy}m(z)|^2\prec  W^{-1}\eta^{-1/2}+W^{-1}\prec  W^{-1}\eta^{-1/2}$$
\subsection*{7.4 Theorem 4 - Delocalization}
\begin{boxtheorem}{Theorem 4: (Delocalization).}
For any $\ell\ll N$ and fixed $\epsilon, \kappa, c>0$: $$\frac{|\mathcal{A}_{\epsilon, \ell, \kappa}|}{N}\lesssim \sqrt{\epsilon}+\mathcal{O}(N^{-c})$$
\end{boxtheorem}
\textit{Proof} - The following proof is entirely due to Erd\H{o}s, et. al. \cite{21}, where it appears as Proposition 7.1. We present it here in order to better understand the nature of delocalization. The authors assume that $\Lambda(z) = \max_{x, y}|G_{xy}(z)-\delta_{xy}m(z)|\prec \Psi$, where $\Psi$ is a deterministic admissible parameter if $M^{-1/2}\leq \Psi^{(N)}(z)\leq M^{-\gamma/2}$ for all $N$, $E\in [-2+\kappa, 2-\kappa]$ and $\eta\in M^{-1+\gamma}\leq \eta\leq 10$, where $M = \frac{1}{\max_{i, j}S_{ij}}$ and $\kappa>0$ is globally fixed. In the context of the work by Dubova and Yang we have presented so far, these assumptions are satisfied, given that Theorem 4 implies $|G_{xy}(z)-\delta_{xy}m(z)|^2\prec W^{-1}\eta^{-1/2}\lesssim N^{-1}\eta^{-1}$ by using the global diffusion scale $\eta\asymp W^2 N^{-2}$. Furthermore, by the other assumption $N\ll W^{11/8}$, one has $N^{-1}\eta^{-1}\asymp NW^{-1}\ll W^{-5/8}$\cite{bandSDE}. Namely, by Ward and the latter admissible parameter, we have for all $x$: \begin{equation*}\frac{\eta}{\im m}\sum_y|G_{yx}|^2 = \frac{\im G_{xx}}{\im m}\lesssim 1+O(\Psi)\tag{7.4.1}\end{equation*}
uniformly in $E\in [-2+\kappa, 2-\kappa]$. Hence, the map $y\mapsto \frac{\eta}{\im m(z)}|G_{yx}|^2$ is approximately a PDF on $\Gamma$, yielding:
$$\frac{\eta}{\im m(z)}\|P_{x, \ell}G \mathbf{e}_x\|^2 = \frac{\eta}{\im m(z)}\sum_y \mathbf{1}\left(|y-x|\geq \ell\right)|G_{yx}|^2=$$
\begin{equation*}=\frac{\eta}{\im m(z)}\sum_y|G_{yx}|^2 - \frac{\eta}{\im m(z)}\sum_y \mathbf{1}\left(|y-x|\geq \ell\right)|G_{yx}|^2=1+O(N^{-c}),\tag{7.4.2}\end{equation*}
for some $c>0$ by using Theorem 4, Lemma B.1 and $(7.4.1)$. Using the spectral decomposition $(1.1)$: 
\begin{equation*}\frac{\eta}{\im m(z)} \|P_{x, \ell} G\mathbf{e}_x\|^2 = \frac{\eta}{\im m(z)}\left\|\sum_\alpha \frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)P_{x, \ell}\mathbf{u}_\alpha\right\|^2\leq \mathcal{L}+\mathcal{R}=\tag{7.4.3}\end{equation*}
$$= \frac{\eta}{\im m(z)}\left(1+\frac{1}{\xi}\right)\left\|\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}\frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)P_{x, \ell}\mathbf{u}_\alpha\right\|^2 +  \frac{\eta}{\im m(z)}\left(1+\frac{1}{\xi}\right)\left\|\sum_{\alpha\in \mathcal{A}^C_{\epsilon, \ell}}\frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)P_{x, \ell}\mathbf{u}_\alpha\right\|^2,$$
where $\xi>0$ is arbitrary and $\mathcal{A}^C_{\epsilon, \ell} =\{1, \cdots, N\}\backslash A_{\epsilon, \ell}$ is the complement set. We can bound the left $\mathcal{L}$ term, using $(2.1)$ and Lemma A.1:
$$\mathcal{L}\leq \frac{\eta}{\im m(z)}\left\|\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}\frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)\mathbf{u}_\alpha\right\|^2\leq \frac{\eta}{\im m(z)}\sum_\alpha\frac{|u_\alpha(x)|^2}{|\lambda_\alpha-z|^2} = \frac{\im G_{xx}}{\im m(z)}\lesssim 1 + O(\Psi)$$
$$\Rightarrow \mathcal{L}\leq \frac{\eta}{\im m(z)}\left\|\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}\frac{1}{\lambda_\alpha -z}\overline{u}_\alpha(x)\mathbf{u}_\alpha\right\|^2\leq (1+O(\Psi))\sqrt{\frac{\eta}{\im m(z)}}\left|\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}\frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)P_{x, \ell}\mathbf{u}_\alpha\right\|\leq$$
\begin{equation*}\leq (C+O(\Psi))\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}\sqrt{\frac{\eta}{(E-\lambda_\alpha)^2+\eta^2}}|u_\alpha(x)|\|P_{x, \ell}\mathbf{u}_\alpha\|\tag{7.4.4}\end{equation*}
By the same token, we get the following bound on $\mathcal{R}$:

\begin{equation*} \tag{7.4.5}\mathcal{R}\leq \left\|\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}^C}\frac{1}{\lambda_\alpha-z}\overline{u}_\alpha(x)\mathbf{u}_\alpha\right\|^2 = \sum_{\alpha\in \mathcal{A}_{\epsilon, \ell})}\frac{|u_\alpha(x)|^2}{|\lambda_\alpha-z|^2}\end{equation*}
Putting all the results we got, namely $(7.4.3), (7.4.3), (7.4.4)$ and $(7.4.5)$, we get uniformly on $E\in [-2+\kappa, 2-\kappa]$: 
$$1+O(N^{-c})\leq (C+O(N^{-c}))\left(1+\frac{1}{\xi}\right)\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}\sqrt{\frac{\eta}{(E-\lambda_\alpha)^2+\eta^2}}|u_\alpha(x)|\|P_{x, \ell}\mathbf{u}_\alpha\|+$$
$$+(1+\xi)\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}^c}\frac{\eta|u_\alpha(x)|^2}{\im m(z)|\lambda_\alpha-z|^2}$$
Using the fact that$\int_{[-2+\kappa, 2-\kappa]}dR\frac{\eta}{(E-\lambda_\alpha)^2+\eta^2}\geq \frac{\pi}{2}$, we can use Jensen's inequality:
$$1+O(N^{-c})\leq (C+O(N^{-c}))\left(1+\frac{1}{\xi}\right)\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}}|u_\alpha(x)|\|P_{x, \ell}\mathbf{u}_\alpha\|+$$
\begin{equation*}+(1+\xi)\frac{1}{4-2\kappa}\int_{[-2+\kappa, 2-\kappa]}dE\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}^c}\frac{\eta|u_\alpha(x)|^2}{\im m(z)|\lambda_\alpha-z|^2}\tag{7.4.6}\end{equation*}
We can use the trace inequality to show that: 
$$\frac{1}{4-2\kappa}\int_{[-2+\kappa, 2-\kappa]}\frac{dE}{N}\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}^c}\frac{\eta|u_\alpha(x)|^2}{\im m(z)|\lambda_\alpha-z|^2}\leq \frac{1}{4-2\kappa} \int dE \frac{1}{N}\frac{\im \text{Tr }G}{\im m(z)} = 1+O(\Psi)$$
Using this, we can average out $(7.4.6)$ with $N^{-1}\sum_x$:
$$\Rightarrow \frac{1}{4-2\kappa}\int dE \frac{1}{N}\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}^C}\frac{\eta}{\im m(z)|\lambda_\alpha-E-i\eta|^2}\geq 1-(C+O(N^{-c}))\sqrt{\epsilon})\sqrt{\epsilon}-O(N^{-c})\geq 1-C\sqrt{\epsilon}-O(N^{-c})$$
$$\Rightarrow \frac{1}{4-2\kappa}\int dE \frac{1}{N}\sum_{\alpha\in \mathcal{A}_{\epsilon, \ell}^C}\frac{\eta}{\im m(z)|\lambda_\alpha-E-i\eta|^2}\leq C\sqrt{\epsilon}+O(N^{-c}),$$
where we set $\xi =\sqrt{\epsilon}$.
